Test SUSIE for regions near genes (500kb flanking)

### 2020-06-21 analysis/simulation-susie-ukbchr22-gtex.adipose.Rmd
reduce mr.ash memory/mr.ashs

```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200503/"
outputdir <- "~/causalTWAS/simulations/simulation_susietest_20200604/"
mr.ash2dir <-  "~/causalTWAS/simulations/simulation_ashtest_20200527/"
```

## Simulation 1
Priors:
```{r para 1}
readLines(paste0(outputdir, "prior-1.R"))
```

SUSIE results:
```{r sim 1 setup}
mrashtag <- "20200527-1"
susietag <- "20200604-1"
mrashres.gene <- paste0(mr.ash2dir, mrashtag, "-mr.ash2s.expr-res.expr.txt")
mrashres.snp <- paste0(mr.ash2dir, mrashtag, "-mr.ash2s.expr-res.snp.txt")
```

### FALSE positives in mr.ash2

```{r sim 1 3, out.width = "98%", out.height="95%"}
name <- "DGCR14"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

```{r sim 1 4, out.width = "98%", out.height="95%"}
name <- "VPREB3"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

```{r sim 1 5, out.width = "98%", out.height="95%"}
name <- "TCN2"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

### FALSE negatives in mr.ash2
```{r sim 1 6, out.width = "98%", out.height="95%"}
name <- "CBX6"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

```{r sim 1 7, out.width = "98%", out.height="95%"}
name <- "CHEK2"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

### True positives in mr.ash2
```{r sim 1 8, out.width = "98%", out.height="95%"}
name <- "LMF2"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

```{r sim 1 9, out.width = "98%", out.height="95%"}
name <- "DDX17"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```
```{r sim 1 10, out.width = "98%", out.height="95%"}
name <- "MIF"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

## Simulation 3
Priors:
```{r para 3}
readLines(paste0(outputdir, "prior-3.R"))
```

SUSIE results:
```{r sim 3 setup}
mrashtag <- "20200527-3"
susietag <- "20200604-3"
mrashres.gene <- paste0(mr.ash2dir, mrashtag, "-mr.ash2s.expr-res.expr.txt")
mrashres.snp <- paste0(mr.ash2dir, mrashtag, "-mr.ash2s.expr-res.snp.txt")
```
```{r sim 3 1, out.width = "98%", out.height="95%"}

name <- "MCM5"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

```{r sim 3 2, out.width = "98%", out.height="95%"}

name <- "CBX6"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

>>>>

```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200616/"
outputdir <- "~/causalTWAS/simulations/simulation_susietest_20200616/"
mr.ash2dir <-  "~/causalTWAS/simulations/simulation_ashtest_20200616/"
```

## Simulation 1
Priors:
```{r para 1}
mrashtag <- "20200616-1"
susietag <- "20200616-1"
readLines(paste0(outputdir, "prior-", susietag, ".R"))
```

```{r sim 1 setup}
mrashres.gene <- paste0(mr.ash2dir, mrashtag, "-mr.ash2s.expr-res.expr.txt")
mrashres.snp <- paste0(mr.ash2dir, mrashtag, "-mr.ash2s.expr-res.snp.txt")
```

### SUSIE results: PIP > 0.5 or causal genes

```{r sim 1 examples, out.width = "98%", out.height="95%"}
nameall <- read.table(paste0(outputdir, "gene-flank500kb-", susietag, ".txt"))[ , 4]
for (name in nameall){
  susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
  print(paste0("SUISE results for regions around ", name))
  plot_all(susieres, mrashres.gene, mrashres.snp)
}
```
